Benchmarking figures

### 2016-05-04 results/figures.Rmd
lofreq pipeline is a go and in makefile
work updating  Rmd for lofreq

---
title: "Benchmarking figures"
output: pdf_document
---

```{r,settings_and_lib,echo=F,message=F,}
require(ggplot2)
require("plyr")
require("Biostrings")
require(reshape2)
require("pROC")
require(gridExtra)
require(cowplot)
require(gtable)
require(png)
theme_set(new = theme_classic())
require(knitr)
opts_chunk$set(fig.align = "center", warning = FALSE, echo = FALSE,message=F,cache=T)

@@

lofreq.df<-read.csv("../data/process/2015-6-23/lofreq/all.removed.mapq_vcf.vcf_csv.csv",stringsAsFactors = F)

lofreq.df$category[lofreq.df$mutation %in% wt_mut]<-"wt"
lofreq.df$categroy[lofreq.df$mutation %in% mfe.df$mutation]<-"mfe"

lofreq.df$p.val<-lofreq.df$QUAL # to make the roc based on the quality scores given by lofreq

lofreq.roc<-hiseq.roc(lofreq.df,possible_tp,possible_vars,"<")

>>>>

---
title: "Benchmarking figures"
output: github_document
---

```{r,settings_and_lib,echo=F,message=F,}
require(ggplot2)
require("plyr")
require("Biostrings")
require(reshape2)
require("pROC")
require(gridExtra)
require(cowplot)
require(gtable)
require(png)
require(grid)
theme_set(new = theme_classic())
require(knitr)
opts_chunk$set(fig.align = "center", warning = FALSE, echo = FALSE,message=F,cache=T)

@@

lofreq.df<-read.csv("../data/process/2015-6-23/Lofreq/lofreq_csv/all.lofreq.csv",stringsAsFactors = F,comment.char="#")

lofreq.df<-mutate(lofreq.df,mutation=paste0(CHROM,"_",REF,POS,ALT))
lofreq.df<-mutate(lofreq.df,category=mutation %in% true_snv$mutant,Id=ID)
lofreq.df$category[lofreq.df$mutation %in% wt_mut]<-"wt"
lofreq.df$category[lofreq.df$mutation %in% mfe.df$mutation]<-"mfe"

lofreq.df$p.val<-as.numeric(lofreq.df$QUAL) # to make the roc based on the quality scores given by lofreq
lofreq.roc<-hiseq.roc(lofreq.df,possible_tp,possible_vars,"<")
